---
title: "STA101 Schedule"
subtitle: Spring 2023
output:
  html_document:
    css: custom-site.css
    df_print: paged
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, eval=F)
```

```{r load-libraries}
library(tidyverse)
library(knitr)
#library(emo)
```

```{r smart-date-setup}
# set these:
firstDay = as.Date("2023-01-12")
firstDayID = "Thu"
lastDay = as.Date("2023-04-25")
lectureDays = c("Tue", "Thu")
labDays = c("Fri")
holidays = as.Date(c("2023-01-16", "2023-03-13 - 2023-03-17"))
### render table
allDates = seq(from = firstDay, to = lastDay, by = 'day')
schedule = data.frame(allDates,
                        dayOfWeek = weekdays(allDates, abbreviate=T)) %>%
  filter(dayOfWeek %in% c(lectureDays, labDays))
schedule = schedule %>%
  mutate(lab = ifelse(dayOfWeek %in% labDays, TRUE, FALSE)) %>%
  mutate(Topic = ifelse(allDates %in% holidays, "NO CLASS", "")) %>%
  mutate(Date = format(allDates, format = "%b %d")) %>%
  mutate(Date = paste(dayOfWeek, Date)) %>%
  mutate(Week = rep("", nrow(schedule))) %>%
  mutate(Prepare = rep("", nrow(schedule))) %>%
  mutate(AE = rep("", nrow(schedule))) %>%
  mutate(Assignment = rep("", nrow(schedule))) %>%
  mutate(Exam = rep("", nrow(schedule))) %>%
  mutate(Project = rep("", nrow(schedule))) %>%
  select(Week, Date, Topic, Prepare, AE, Assignment, Exam, Project)
# to be pasted into console then pasted into markdown:
schedule %>%
  kable(format = "markdown")
```

Find all assignments and due dates here. This schedule updates frequently. 

|Week |Date       |Topic |Prepare |Notes |Assignment |Exam |Project |
|:----|:----------|:-----|:-------|:--|:----------|:----|:-------|
|     |Thu Jan 12 |Welcome to STA 101!|        |   |           |     |        |
|     |Fri Jan 13 |Hello R!      |        |   |           |     |        |
|     |Tue Jan 17 |Exploring Data I      |        |   |           |     |        |
|     |Thu Jan 19 |Exploring Data II      |        |   |           |     |        |
|     |Fri Jan 20 |Exploring Data Lab      |        |   |           |     |        |
|     |Tue Jan 24 |Exploring Data III      |        |   |           |     |        |
|     |Thu Jan 26 |Manipulating Data      |        |   |           |     |        |
|     |Fri Jan 27 |Manipulating Data      |        |   |           |     |        |
|     |Tue Jan 31 |      |        |   |           |     |        |
|     |Thu Feb 02 |      |        |   |           |     |        |
|     |Fri Feb 03 |      |        |   |           |     |        |
|     |Tue Feb 07 |      |        |   |           |     |        |
|     |Thu Feb 09 |      |        |   |           |     |        |
|     |Fri Feb 10 |      |        |   |           |     |        |
|     |Tue Feb 14 |      |        |   |           |     |        |
|     |Thu Feb 16 |      |        |   |           |     |        |
|     |Fri Feb 17 |      |        |   |           |     |        |
|     |Tue Feb 21 |      |        |   |           |     |        |
|     |Thu Feb 23 |      |        |   |           |     |        |
|     |Fri Feb 24 |      |        |   |           |     |        |
|     |Tue Feb 28 |      |        |   |           |     |        |
|     |Thu Mar 02 |      |        |   |           |     |        |
|     |Fri Mar 03 |      |        |   |           |     |        |
|     |Tue Mar 07 |      |        |   |           |     |        |
|     |Thu Mar 09 |      |        |   |           |     |        |
|     |Fri Mar 10 |      |        |   |           |     |        |
|     |Tue Mar 14 |NO CLASS: SPRING BREAK      |        |   |           |     |        |
|     |Thu Mar 16 |NO CLASS: SPRING BREAK      |        |   |           |     |        |
|     |Fri Mar 17 |NO LAB: SPRING BREAK      |        |   |           |     |        |
|     |Tue Mar 21 |      |        |   |           |     |        |
|     |Thu Mar 23 |      |        |   |           |     |        |
|     |Fri Mar 24 |      |        |   |           |     |        |
|     |Tue Mar 28 |      |        |   |           |     |        |
|     |Thu Mar 30 |      |        |   |           |     |        |
|     |Fri Mar 31 |      |        |   |           |     |        |
|     |Tue Apr 04 |      |        |   |           |     |        |
|     |Thu Apr 06 |      |        |   |           |     |        |
|     |Fri Apr 07 |      |        |   |           |     |        |
|     |Tue Apr 11 |      |        |   |           |     |        |
|     |Thu Apr 13 |      |        |   |           |     |        |
|     |Fri Apr 14 |      |        |   |           |     |        |
|     |Tue Apr 18 |      |        |   |           |     |        |
|     |Thu Apr 20 |      |        |   |           |     |        |
|     |Fri Apr 21 |      |        |   |           |     |        |
|     |Tue Apr 25 |      |        |   |           |     |        |